### 2021-07-28 README.Rmd
Added functions to assist in auto-conditioning.

* 2021_07-04 aMSE 0.0.0.1500 Another big change. Functions added to aid conditioning, and aspects of the projections streamlined.  No errors, warnings, or notes

* 2021-07-04 aMSE 0.0.0.1900 More big changes. I have removed the numbers-at-size large matrices from the zoneDP object into a NAS object. zoneDP is now only 12Mb instead of 450Mb and so can now be stored conveniently for each run. In addition, fixed recruitment deviates have now been implemented (although the default is to not use them - all are set to -1). But, expreimentally, in Tasmania, setting the deviate in 1991 = 2.0 meaning that the base level of recruitment off the recruitment curve is doubled, improves the relationship between predicted cpue and observed cpue so this holds great promise for improved conditioning.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
rundir <- paste0(ddir,"aMSEUse/scenarios/HS652510")
datadir <- paste0(ddir,"aMSEUse/scenarios/tasdata")
alldirExists(rundir,datadir,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# run the scenario --------------------- Obviously unhash this to make it work
#out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,
#              hcrfun=mcdahcr,sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#              getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=32,
#              cleanslate=TRUE,verbose=TRUE,doproject=TRUE,ndiagprojs=3)
# make results webpage ---------------------------------------------------------
# replist <- list(starttime=as.character(out$starttime),
#                 endtime=as.character(out$projtime))
# glb <- out$glb
# runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
#                    "  replicates = ",glb$reps,",   years projected = ",glb$pyrs,
#                    "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
#                    "  Randomseed for conditioning = ",out$ctrl$randseed)
# Unhash the make_html command to generate the results webspage
# make_html(
#   replist = replist,
#   rundir = rundir,
#   width = 500,
#   openfile = TRUE,
#   runnotes = NULL,
#   verbose = FALSE,
#   packagename = "aMSE",
#   htmlname = "hs652510"
# )

>>>>

* 2021_07-28 aMSE 0.0.0.800 Added functions (changecolumn, getrecdevcolumn, gettasdevssq) to assist in automated operating model conditioning on the fishery. Also modified the biology_plots and oneyear and oneyearcat to assist with speeding the processes. Lots of additional minor changes but some important ones to do_MSE (read the help, ?do_MSE).

* 2021-07-20 aMSE 0.0.0.900 Added do_condition and compareCPUE. Both used to speed the conditioning of the operating model, though a number of developments are still under development. Currently can automatically search for the AvRec value that will optimize the sum-of-squared residual fit between the
observed CPUE in the historical period, and those predicted by the conditioned model. The undeveloped bit related to the ad hoc recruitment deviates.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/aMSEUse/scenarios/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/aMSEUse/scenarios/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
postdir <- "testnew"  # also used to label the output HTML file 
rundir <- paste0(ddir,postdir)
datadir <- paste0(ddir,"tasdata")
alldirExists(rundir,datadir,verbose=verbose)
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# HarvestStrategy.R should be in datadir, if it is to be shared by scenarios
source(paste0(datadir,"/TasmanianHS.R"))
# run the scenario --------------------- Obviously unhash this to make it work
# out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,hcrfun=mcdahcr,
#                  sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#                  getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=50,
#                  cleanslate=TRUE,verbose=TRUE,doproject=doproject,ndiagprojs=4,
#                  openfile=TRUE,savesauout=FALSE)
# make results webpage ---------------------------------------------------------
# replist <- list(starttime=as.character(out$starttime),
#                 endtime=as.character(out$projtime))
# glb <- out$glb
# projy <- ifelse(doproject,glb$pyrs,0)
# runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
#                    "  replicates = ",glb$reps,",   years projected = ",projy,
#                    "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
#                    "  Randomseed for conditioning = ",out$ctrl$randseed)
# 
# make_html(replist = replist,  rundir = rundir,  width = 500,  openfile = TRUE,
#           runnotes = runnotes,   verbose = FALSE,  packagename = "aMSE",
#           htmlname = postdir)
